data cleaning logs

### 2021-06-16 conditions.Rmd
Changes to the conditions scripts

```{r}
# read data from excel file
library(readr)
library(tidyverse)

library(readxl)

df <- read_excel("C:/Users/Evelyn GAKINYA/Documents/2. Data cleaning/data cleaning scripts/input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx")

@@

@@

```{r}
df_1 <- df %>% 
        mutate(cluster_id = paste(enumeration_area,locality_code,oslo_area, sep = "")) %>% 
        dplyr::select(enumeration_area, locality_code, oslo_area,cluster_id)
head(df_1)

@@

@@

```
```{r}
df4 <- df %>% 
  filter(childlabour_check == "Flagged") %>% 
        dplyr::select(childlabour_check,child_labour, tot_children, under_18_working)
df4
```

@@

```{r}
##Flag if reported shelter is tent, but HH reports having defects related to windows, floors, or foundation
df <- df %>%
      mutate(tent_check = case_when(df$shelter_type_inperson == "tent" & (shelter_issues !="none")~ "Flagged", TRUE ~ "" ))
```
```{r}
df12 <- df %>% 
      filter(tent_check == "Flagged") %>% 
       dplyr::select(tent_check, shelter_type_inperson, shelter_issues)
head(df12)
```

```{r}
##Flag if any expenditure other than food is more than 50% of monthly expenditure
#df <- df %>%
   #mutate(expense_check = case_when( (as.numeric(df$water_exp) | as.numeric(df$rent_exp) | as.numeric(df$medical_exp) | #as.numeric(df$fuel_exp)) >= 0.5*(as.numeric(df$tot_expenses))~ "Flagged", TRUE ~ "" ))
```
```{r}
df <- df %>%
   mutate(expense_check = case_when( df$water_exp | df$rent_exp | df$medical_exp | df$fuel_exp >= 0.5*(df$tot_expenses)~ "Flagged", TRUE ~ "" ))
```

@@

```{r}
df17 <- df %>% 
  filter(gender_check == "Flagged") %>% 
  dplyr::select(gender_check, gender_respondent_r, gender_respondent_r2)
df17
```
```{r}
shati
bureij
deir_balah_camp
jabalya_camp
khan_yunis_camp
maghazi
nuseirat_camp
rafah_camp

```{r}
##Flag if selected HH lives in Refugee camp, but municipality selected not a camp
df <- df %>% 
      mutate(camp_check = case_when(df$camp == "yes" &  (df$hh_location_gaza != "shati"| df$hh_location_gaza !="bureij" | df$hh_location_gaza != "deir_balah_camp" | df$hh_location_gaza !="jabalya_camp" | df$hh_location_gaza != "khan_yunis_camp"| df$hh_location_gaza != "maghazi"| df$hh_location_gaza != "nuseirat_camp" | df$hh_location_gaza != "rafah_camp" )~ "Flagged", TRUE ~ ""))
```
```{r}
df19 <- df %>% 
        filter(camp_check == "Flagged") %>% 
       dplyr::select(camp_check,hh_location_gaza,camp)
df19
```

@@

```{r}
df20 <- df %>% 
      filter(covid_check == "Flagged") %>% 
     dplyr::select(covid_check,`treatment_required/covid_19_treatment`,`treatment_required/covid_19_testing`, treatment_required)
df20
```
```{r}
library(Hmisc)
df <- df %>% 
     mutate(health_barrier_check = case_when(location == "gaza" & (obstructive_barriers %nin% health_barriers) ~ "Flagged", TRUE ~ ""))
```

@@

>>>>

```{r}
# read data from excel file

library(readr)
library(tidyverse)
library(Hmisc)
library(readxl)

##df <- read_csv("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.csv")

@@

df <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_-_all_versions_-_False_-_2021-06-16-07-13-11.xlsx")

@@

```{r}
library(dplyr)
df_2 <- df %>% 
          mutate(cluster_id = if_else(is.na(oslo_area),
            paste(enumeration_area,locality_code, sep = ""),
            paste(enumeration_area,locality_code,oslo_area, sep = ""))) %>%
            dplyr::select(cluster_id,enumeration_area,locality_code, oslo_area )
head(df_2)

@@

```{r}
library(dplyr)
df_3 <- df %>% 
          mutate(
            oslo_area =replace(oslo_area,is.na(oslo_area), "gaza"),
            cluster_id =paste(enumeration_area,locality_code,oslo_area, sep = "_")) %>%
            dplyr::select(cluster_id,enumeration_area,locality_code, oslo_area )
head(df_3)
```

@@

```
```{r}
df4 <- df %>% 
  #filter(childlabour_check == "Flagged") %>% 
        dplyr::select(childlabour_check,child_labour, tot_children, under_18_working)
df4
```

@@

```{r}
##Flag if reported shelter is tent, but HH reports having defects related to windows, floors, or foundation
df <- df %>%
      mutate(tent_check = case_when(df$shelter_type_inperson == "tent" & (shelter_issues !="none")~ "Flagged", TRUE ~ "" ))
```
```{r}
df12 <- df %>% 
      #filter(tent_check == "Flagged") %>% 
       dplyr::select(tent_check, shelter_type_inperson, shelter_issues)
head(df12)
```

```{r}
##Flag if any expenditure other than food is more than 50% of monthly expenditure
df <- df %>%
   mutate(expense_check = case_when( (as.numeric(df$water_exp) | as.numeric(df$rent_exp) | as.numeric(df$medical_exp) | as.numeric(df$fuel_exp)) >= 0.5*(as.numeric(df$tot_expenses))~ "Flagged", TRUE ~ "" ))
```
```{r}
##df <- df %>%
   ##mutate(expense_check = case_when( df$water_exp | df$rent_exp | df$medical_exp | df$fuel_exp >= 0.5*(df$tot_expenses)~ ##"Flagged", TRUE ~ "" ))
```

@@

```{r}
df17 <- df %>% 
  filter(gender_check == "Flagged") %>% 
  dplyr::select(gender_check, gender_respondent_r, gender_respondent_r2)
df17
```

```{r}
##Flag if selected HH lives in Refugee camp, but municipality selected not a camp
df <- df %>% 
      mutate(camp_check = case_when(df$camp == "yes" &  (df$hh_location_gaza != "shati_camp"| df$hh_location_gaza !="bureij_camp" | df$hh_location_gaza != "deir_balah_camp" | df$hh_location_gaza !="jabalya_camp" | df$hh_location_gaza != "khan_yunis_camp"| df$hh_location_gaza != "maghazi_camp"| df$hh_location_gaza != "nuseirat_camp" | df$hh_location_gaza != "rafah_camp" )~ "Flagged", TRUE ~ ""))
```
```{r}
df19 <- df %>% 
        filter(camp_check == "Flagged") %>% 
       dplyr::select(camp_check,hh_location_gaza,camp)
df19
```

@@

```{r}
df20 <- df %>% 
      filter(covid_check == "Flagged") %>% 
     dplyr::select(covid_check,`treatment_required/covid_19_treatment`,`treatment_required/covid_19_testing`, treatment_required)
df20
```
```{r}
df <- df %>% 
     mutate(health_barrier_check = case_when(location == "gaza" & (obstructive_barriers %nin% health_barriers) ~ "Flagged", TRUE ~ ""))
```

@@

```{r}
##Flag if tot_cwd == 0 and drop_out_reason == "Disability"
df <- df %>% 
      mutate(disability_check = case_when( tot_cwd == 0 & drop_out_reason == "Disability" ~ "Flagged", TRUE ~ ""))
```
